% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage[dvipsnames]{xcolor}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
%\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{Kunal Sangani}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{http://jblevins.org/projects/cv-template/}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {economics, macroeconomics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 9in},
  left=1.0in,
  top=1.0in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\large\scshape}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}
\setlist[enumerate]{wide=0pt, leftmargin=20pt, labelwidth=10pt, align=left}


% Paper command for easy paper input
\newcommand{\paper}[2]{``\href{#2}{#1}''}
\newcommand{\academicpaper}[1]{\textcolor{Blue}{\textbf{``#1''}}}
\newcommand{\journal}[1]{\textbf{\textit{#1}}}

\begin{document}

% Place name at left
{\Large \textbf{\name}}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}{0.45\linewidth}
  %Wyss Hall \\
  20 N Harvard Street  \\
  Boston, MA 02163
\end{minipage}
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{ll}
    %Phone: & (315) 382-5338 \\
    Email: & \href{mailto:8ksangani@gmail.com}{\tt 8ksangani@gmail.com} \\
    Homepage: & \href{https://kunalsangani.com}{\tt https://kunalsangani.com} \\
  \end{tabular}
\end{minipage}

\section*{Employment}
\begin{description}[labelindent=0pt, labelwidth=1in, labelsep*=1em, leftmargin =!, font=\normalfont]
\item[2025--] Northwestern University, Department of Economics\\
Assistant Professor
\item[2024--2025] Stanford Graduate School of Business\\
Lazear-Liang Postdoctoral Fellow
\end{description}

\section*{Education}
\begin{description}[labelindent=0pt, labelwidth=1in, labelsep*=1em, leftmargin =!, font=\normalfont]
\item[2019--2024] Ph.D. in Business Economics and M.A. in Economics, Harvard University\\
Committee: Gabriel Chodorow-Reich (chair), Ludwig Straub, Andrei Shleifer
\item[2012--2016] B.A. in Economics {with Honors and Distinction}, Stanford University\\
\end{description}

\section*{Past Employment}
\begin{description}[labelindent=0pt, labelwidth=1in, labelsep*=1em, leftmargin =!, font=\normalfont]
\item[2018--2019] Bolt (payments start-up), Operations
\item[2017--2018] The Boston Consulting Group, Associate
\item[2016] White House Council of Economic Advisers (CEA), Intern
\item[2016] Google, Associate Product Management (APM) Intern
\end{description}

\section*{Academic Papers}
\begin{enumerate}
\item \academicpaper{Quotas in General Equilibrium} {with David Baqaee.} 
\item \academicpaper{Complete Pass-Through in Levels.} 
\item \academicpaper{Pass-Through in Levels and the Unequal Incidence of Commodity Shocks.} 
\item \academicpaper{Markups Across the Income Distribution: Measurement and Implications.} 
\item \academicpaper{The Market Impact of Fed Communications: The Role of the Press Conference} 
{with Namrata Narain.}\\
Accepted, \journal{International Journal of Central Banking.}
%\\ \textit{Media}: Wall Street Journal, Financial Times, Bloomberg, Brookings, Marketwatch, Bloomberg Opinion, Semafor, Investopedia 
\item \academicpaper{The Darwinian Returns to Scale} 
{with David Baqaee and Emmanuel Farhi.}\\ 
\journal{Review of Economic Studies}, 91 (3) 2024: 1373--1405.
\item \academicpaper{The Supply-Side Effects of Monetary Policy} 
{with David Baqaee and Emmanuel Farhi.}\\ 
\journal{Journal of Political Economy}, 132 (4) 2024: 1065--1112.
\end{enumerate}

\section*{Other Writing}
\begin{enumerate}
\item \paper{Evidence---and an explanation---for the recent surge in inflation inequality.}{https://cepr.org/voxeu/columns/evidence-and-explanation-recent-surge-inflation-inequality} \textit{VoxEU}, December 2023.
\item \paper{The market impact of the Fed press conference.}{https://cepr.org/voxeu/columns/market-impact-fed-press-conference} With Namrata Narain. \textit{VoxEU}, March 2023.
\item \paper{Darwinian reallocations and the origins of aggregate increasing returns to scale.}{https://cepr.org/voxeu/columns/darwinian-reallocations-and-origins-aggregate-increasing-returns-scale} With David Baqaee. \textit{VoxEU}, August 2021.
\item \paper{Monetary policy and productivity: A new transmission channel.}{https://cepr.org/voxeu/columns/monetary-policy-and-productivity-new-transmission-channel} With David Baqaee and Emmanuel Farhi. \textit{VoxEU}, January 2021.
\item \paper{Impact investing in developing countries: Legal institutions and work-arounds.}{https://law.stanford.edu/wp-content/uploads/2019/10/Impact-Investing-In-the-Absence-of-Credible-Legal-Institutions-15-16-Final-Report.pdf} With Paul Brest, Shereen Griffith, Damira Khatam, Demoni Newman, Reirui Ri, Alessandra Santiago, Mengyi Xu, and Lucie Zikova. \textit{Stanford Law School Law and Policy Lab}, December 2015.
\end{enumerate}

\section*{Fellowships \& Awards}
\begin{description}[labelindent=0pt, labelwidth=1in, labelsep*=1em, leftmargin =!, font=\normalfont]
\item[2024] Padma Desai Prize for Economic Research, Harvard 
\item[2021] Harvard Bok Center Certificate of Distinction in Teaching
\item[2021] John M. Olin Fellowship in Empirical Law and Finance
\item[2016] J. E. Wallace Sterling Award (Top 25 graduates in School of Humanities and Sciences)
\item[2016] Firestone Medal for Senior Thesis in Economics, Stanford
\item[2015] Phi Beta Kappa (junior elect)
\end{description}

\section*{Presentations (including scheduled)}
\begin{description}[labelindent=0pt, labelwidth=1in, labelsep*=1em, leftmargin =!, font=\normalfont]
\item[2025] AEA Annual Meeting, University of Hawaii at Manoa, Federal Reserve Macroeconomics and Monetary Policy Conference (discussant), Stanford Macro Faculty Brownbag, Princeton, Federal Reserve Board, San Francisco Federal Reserve, Stanford FRILLS, Empirical Macro Discussion Group, Stanford Global Capital Allocation Workshop, UCLA, BU Macro Junior Conference, Yale Cowles Conference on International Trade (discussant), Society of Economic Dynamics (SED), NBER Economic Fluctuations \& Growth Summer Meeting, CEBRA Annual Meeting (HBS), Nordic Summer Symposium in Macro, Duke, University of Illinois Urbana-Champaign, NBER Monetary Economics Fall Meeting (discussant), Macro Finance Society Workshop (discussant) %, University of Wisconsin Milwaukee
\item[2024] Northwestern, University of Chicago Booth School of Business, Harvard Kennedy School, Wharton, Boston University, University of Southern California, International Industrial Organization Conference (IIOC), Society of Economic Dynamics (SED), Stanford Graduate School of Business, UCLA, Northwestern, University of Michigan, Minneapolis Fed, Columbia, Brown, UC Berkeley %, CMA?, University of Hawaii Mano'a? 
\item[2023] Chicago Fed Rookie Conference, Society of Economic Dynamics (SED), Bristol Macroeconomics Workshop, Labor, Firms and Macro Workshop
\item[2022] NBER Summer Institute, Marvin S. Goodfriend Conference (Richmond Fed), Labor, Firms and Macro Workshop
\item[2021] Workshop on Firm Dynamics, Market Structures, and Productivity (University of Kent) 
\end{description}

\section*{Teaching}
\begin{description}[labelindent=0pt, labelwidth=1in, labelsep*=1em, leftmargin =!, font=\normalfont]
\item[2021] The Political Economy of Globalization\\ (TA for Prof. Larry Summers and Prof. Robert Lawrence, Harvard) 
\item[2015] Problem Solving and Decision-Making for Social Change\\ (TA for Prof. Paul Brest, Stanford Law School)
\end{description}

\section*{Professional Service}
\begin{description}[labelindent=0pt, labelwidth=1in, labelsep*=1em, leftmargin =!, font=\normalfont]
\item[2020--2021] President, Harvard Graduate Economics Association
\item[Refereeing] {AEJ: Applied Economics, AEJ: Microeconomics, American Economic Review, AER: Insights, B.E. Journal of Macroeconomics, Econometrica, International Journal of Central Banking, International Journal of Industrial Organization, Journal of Economic Dynamics and Control, Journal of Economic Theory, Journal of Money, Credit, and Banking, Journal of Political Economy, JPE Macroeconomics, Journal of the European Economic Association, Macroeconomic Dynamics, Quarterly Journal of Economics, Review of Economics and Statistics, Review of Economic Studies}
\end{description}

%\bigskip

%% Footer
%\begin{center}
%  \begin{footnotesize}
%    Last updated: \today \\
%    \href{\footerlink}{\texttt{\footerlink}}
%  \end{footnotesize}
%\end{center}

\end{document}
